SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-10 docs/questioning.tex
added material on security and ease of use

@@

>>>>

The value of a detection mechanism as a practical tool depends on how
it is to deploy it in a production setting. That is independent of the
value of a detection mechanism as a research finding. Devising a
mechanism to detect a hitherto undetectable class of attacks may be an
excellent research contribution that merits publication; it may also
be heavily cited and open the road to other, practical
implementations in the future.

The ease of use, in turn, depends on several factors. The detection
mechanism may be deployed server-side or client-side, or both.
Deployments on just the server or the client are easier to handle than
deployments on both of them. The mechanism may be an add-on, or
plugin, on existing software, client or server, or it may be tightly
integrated with existing software, requiring rebuilding from source
code.

No matter where it gets installed, the means of installation influences
ease of use. A detection mechanism that comes with ready to install
packages will trump a detection mechanism that only exists in the form
of source code.

@@

Defenders and attackers are often caught in a cat-and-mouse game,
where countermeasures are bypassed by canny attacks, which are caught
by more sophisticated countermeasures, yet again bypassed by cannier
attacks, and so on. We use Security to refer to the ability of a
detection mechanism to resist being circumvented.

A mechanism that has not been bypassed is not eternally secure, as it
is possible that a bypass method will be discovered in the future. We
examine the various approaches on the knowledge we have to this date,
that is, whether there are known ways to bypass the detection
mechanism today.
